SI for ``Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers''

### 2018-10-17 reports/si.tex
short discussion of the correlations

These incidate the correlations present between the fitted parameters of the chemically-consistant model.
Particularly noteworthy is the positive correlation between the head thickness, $d_h$, and the solvent concentration in the head layer, $\phi_h$, which shows a clear interaction between these two variables.
This can be rationalised as the smoothing of the interface between the head and the solvent, blurring the values of each variable.
Additionally, it is noted that the correlations present are more substantial for the smaller lipid (particularly DLPC), this is due to the reduced structure presented for such a short tailed lipid and the fact that the length of the tail is closer to the value of the surface roughness for DES (\SI{3.3}{\angstrom}\cite{Sanchez-Fernandez2016}).

>>>>

These two-dimensional PDFs give information about the correlations between the parameters fitted to the chemically-consistent model.
The less circular in nature the 2-D PDF is, the greater the correlation present between the respective variables.
Particularly noteworthy is the substantial positive correlation between the head thickness, $d_h$, and the solvent concentration in the head layer, $\phi_h$, across all lipids.
This interaction can be rationalised as being the result of the SLD of the solvent and the head layer (including some fraction of solvent) being similar.
Such a correlation is unavoidable without considering many neutron contrasts of the lipid and solvent due to the solvophilic nature of the lipid heads.
Additionally, it is noted that the correlations present are more substantial for the smaller lipid (particularly DLPC), this is due to the reduced structure presented for such a short tailed lipid and the fact that the length of the tail is closer to the value of the surface roughness for DES (\SI{3.3}{\angstrom}\cite{Sanchez-Fernandez2016}).
